Solar jet observed at the limb in SDO/SST

### 2016-08-10 paper/ms_temp_paper.tex
add temperature imaging

%double check this section
Evidently, the maximum extent of this feature is in SDO $30.4$ and maximises at $12.6$ Mm although the measurements in H$\alpha$ may exceed this were it to be fully visible.
Interestingly, the length of the jet in the coronal lines does not get larger after the second injection on plasma occurs.
This subsequent acceleration of plasma originates from the same location as that of the initial formation, and on the same scale as the first onset.
However, this drives the tip of the jet even higher than the initial.

% need much more here

@@

@@

We observe a jet-like feature at the solar limb on $21$st June 2012 at $07:30:00$ on the solar limb, centred at $910$, $234$ solar x and y.
We have multiple methods with which to view the feature, CRISPT/SST, the range of AIA/SDO coronal wavelengths and SECCHI/STEREO-A.
We have utilised multiple analysis techniques to build a comprehensive picture of the jet-like features motion and the possible impacts on the atmosphere above it.

From the observation of this feature, we can draw the following conclusions
\begin{itemize}
	\item{This particular feature is visible in H$\alpha$ and He II $30.4$, and thus, is inherently a chromospheric object.}
	\item{The jet has two separate ejections of material.}
	\item{The formation of the jet is observed to be similar to the standard jet formation mechanism.}
	\item{The jet has a rotational component to its motion}
\end{itemize}

The feature is observed to extend to $12.6$ Mm in He II $30.4$ nm (and is only found to be shorter in H$\alpha$ due to moving out of the viewing field of view).
Its lifetime is measured of to be $20$ mins and radial velocities are found to be
This very much puts this feature in the ca

The feature is also visible in higher coronal lines, however it does appear just below the solar limb as

>>>>

%double check this section
Evidently, the maximum extent of this feature is in SDO $30.4$ and maximises at $12.6$ Mm although the measurements in H$\alpha$ may exceed this were it to be fully visible.
Interestingly, the length of the jet in the coronal lines does not get larger after the second injection on plasma occurs.

@@

\begin{pycode}[Temp difference]
import numpy as np
import matplotlib.pyplot as plt
from matplotlib.collections import LineCollection
from matplotlib import colors

import sunpy.map
from sunpy.image import slit

from astropy.io import fits
import astropy.units as u

from glob import glob

files = glob('/storage2/temperature_maps/data/full_gauss/*.fits')
files.sort()

def proc_file(x):
    with fits.open(x, memmap=True) as f:
        data = f[0].data[..., 0]
        header = dict(f[0].header)
        m = sunpy.map.Map((data, header))
        m.plotsettings = {'cmap':'coolwarm'}
        crop = m.submap((857.9, 957.94)*u.arcsec,
                 (-197.92, -297.92)*u.arcsec)
    return crop

submaps = []
for afile in files[28:40]:
    temp = proc_file(afile)
    submaps.append(temp)

mc = sunpy.map.Map(submaps, cube=True)

image_1 = slit.slit(mc, [909, 911]*u.arcsec, [-245, -242]*u.arcsec, 1, -1, +1)

temp_values = image_1[0]
temp_inds = image_1[1]

xy_slit = [np.array(zip(range(len(temp_inds)), temp_values[0,:,i])) for i in range(temp_values.shape[2])]

nmap = truncate_colormap(plt.get_cmap('Oranges'), 0.3, 1.0)

line_segments = LineCollection(xy_slit,
                               linewidths=0.25,
                               linestyle='solid',
                               cmap=nmap)

line_segments.set_array(np.arange(len(temp_values[0,0,:])))

fig, ax = plt.subplots()
ax.add_collection(line_segments)
ax_cb = fig.colorbar(line_segments)
ax_cb.set_label('Time')
ax.axis([0,5 , 6.4, 6.6])
ax.set_title('Temperature over slit')
ax.set_xlabel('Distance across slit')
ax.set_ylabel('Temperature')
plt.sci(line_segments)
plt.draw()
plt.show()

@@
